---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# STAT545B

<!-- badges: start -->
<!-- badges: end -->

STAT545B contains the functions created for STAT545B 2021W1. The main function present in this package is `group_counts()` which returns the counts of specified group(s) within a tibble, sorted in decreasing order of count.

## Installation

You can install the development version of STAT545B from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("pattiey/STAT545B", ref = "0.1.0)
```

## Example

This is a basic example which shows you how to use the `group_counts` function in the `STAT545B` package:

```{r example}
library(STAT545B)
suppressMessages(library(tidyverse))
## basic example code
(group_counts(as_tibble(iris), Species))
```
